\documentclass[10pt,fleqn]{article}

%\usepackage[left=1in, right=1in, top=1.2in, bottom=0.9in,includefoot]{geometry}
\usepackage[left=0.8in, right=0.8in, top=0.8in, bottom=0.8in]{geometry}
%\usepackage{fancyhdr}
\usepackage{algorithm2e}
\usepackage[round]{natbib}
\usepackage{amssymb,amstext,amsmath}
\usepackage{booktabs,graphicx}
\usepackage{bm}
\setlength{\parindent}{0mm}
\setlength{\parskip}{3mm}
\input{defs.tex}

%\pagestyle{fancy}  

%% Custom added packages
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{wrapfig}
\usepackage{sidecap}
\usepackage{hyperref}
%% /Custom added packages

%% Initial setup
\hypersetup{
    %bookmarks=true,         % show bookmarks bar?
    %unicode=false,          % non-Latin characters in Acrobat’s bookmarks
    %pdftoolbar=true,        % show Acrobat’s toolbar?
    %pdfmenubar=true,        % show Acrobat’s menu?
    %pdffitwindow=false,     % window fit to page when opened
    %pdfstartview={FitH},    % fits the width of the page to the window
    %pdftitle={My title},    % title
    pdfauthor={Ishan Tembhekar},     % author
    pdfsubject={Resume},   % subject of the document
    %pdfcreator={Creator},   % creator of the document
    %pdfproducer={Producer}, % producer of the document
    %pdfkeywords={keyword1} {key2} {key3}, % list of keywords
    %pdfnewwindow=true,      % links in new window
    %colorlinks=false,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=green,        % color of links to bibliography
    %filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}
%% /Initial setup


%\renewcommand{\headrulewidth}{0.4pt}
%\fancyfoot[C]{\sffamily \thepage{}}
%\fancyhead[C]{\sffamily\footnotesize \textbf{Ishan Tembhekar}  \hfill Ph No: +16269917232 \\\href{mailto:ishan.tembhekar@caltech.edu}{ishan.tembhekar@caltech.edu} \hfill 1200 E. California Blvd, MC 105-50, Pasadena CA 91125 }
%\fancyhead[RL]{}


\begin{document}
%\thispagestyle{fancy}

%\thispagestyle{fancy}
%\fancyhf{} % clear all header and footer fields
%\fancyfoot[C]{\sffamily\thepage}
%\fancyhead[L]{\sffamily\emph{D.\ M.\ Kochmann}}
%\fancyhead[R]{\sffamily\emph{California Institute of Technology}}
%\renewcommand{\headrulewidth}{0.4pt}
%\vspace{-2cm}
%\sffamily

\begin{center}
%\large %$\mathpzc{Curriculum \ Vitae}$\\[0.4cm] %\emph{Curriculum Vitae}
%\scshape Curriculum  Vitae \upshape\\[0.5cm]
\LARGE \textbf{Ishan Tembhekar} \small \\[0.16cm]
1200 E. California Blvd, MC 105-50, Pasadena CA 91125 \\
Phone: +16269917232 \\
\href{mailto:ishan.tembhekar@caltech.edu}{ishan.tembhekar@caltech.edu} \hfill
\end{center}
%\begin{center}\small 
%\emph{California Institute of Technology \\
%Graduate Aerospace Laboratories\\ 
%1200 East California Blvd., MC 105-50, Pasadena, CA 91125 \\
%Phone: 626-991-7232}\\[0.27cm]
%\emph{email:} \href{mailto:ishan.tembhekar@caltech.edu}{\emph{ishan.tembhekar}\rmfamily @\sffamily\emph{caltech.edu}} 
%\end{center}
%\paragraph*{Goal:} Seeking an internship in computational modeling for engineering applications for the summer of 2016  
\paragraph*{Education:}
\vspace{-10pt}
\begin{itemize}
\setlength{\itemsep}{5pt}
\setlength{\parskip}{0pt}
\item[] \textbf{Indian Institute of Technology}, Gandhinagar: \hfill 2012\\
		Bachelor of Technology (B.Tech) in Mechanical Engineering\\
		*\textit{Minor in Computer Science}\\
		GPA: 9.61/10.0 
\item[] \textbf{California Institute of Technology}: \hfill 2014\\
		Master of Science (M.S) in Mechanical Engineering\\
		GPA: 4.0/4.0 
\item[] \textbf{California Institute of Technology}: \hfill  Fall-2017(expected)\\
		Ph.D in Mechanical Engineering 
\end{itemize}
\vspace{-10pt}
%\section*{Areas of Interest}
%Mechanics of Solids, Coarse Grain Atomistics, High performance computing

\paragraph*{Professional Experience:}
\vspace{-10pt}
\begin{itemize}
\setlength{\itemsep}{8pt}
\setlength{\parskip}{0pt}
\item[] \textbf{Graduate Research Assistant}: \emph{Exploring Deformation Mechanisms of Hierarchical Nanolattices} \\
		 Advisor: Prof. Dennis Kochmann, California Institute of Technology \hfill April 2013 - Present 
		  \begin{itemize}
		  \item Developing computational models for studying plastic deformation mechanisms of nanocrystalline materials.
		  \item Building a high-performance parallel C++ code with efficient threading techniques and a distributed memory realization. 
 		  \end{itemize}
\item[] \textbf{Undergraduate Summer Research}: \emph{Fracture toughness enhancement of elastically heterogeneous solids} \\
		  Advisor: Prof. G. Ravichandran, California Institute of Technology \hfill May - July 2011
		   \begin{itemize}
			\item Designed an innovative mechanism for construction of materials having higher resistance to crack propagation than conventional materials.
			\item Conducted experiments to verify the mechanism with successful results.
 			\end{itemize}
\item[] \textbf{Undergraduate Research Assistant}: \emph{Design of a hybrid vehicle with increased fuel efficiency at least rated power}\\		
		  Advisor: Prof. N. Ramakrishnan, IIT Gandhinagar, India \hfill August 2011- April 2012
		   \begin{itemize}
			\item Formed a theoretical framework and constructed a basic prototype of construction of a hybrid vehicle which uses lower rated power than that used in conventional vehicles.
 			\end{itemize} 
\item[] \textbf{Undergraduate Industrial Intern}: \emph{Defect Analysis and Problem Solving} \\
		 Mentor: Mr. B. R. Galgali, DGM, TATA Motors, India \hfill May - July 2010
		    \begin{itemize}
			\item Implemented \emph{Pokayoke} or mistake proofing on various defects observed in the assembly line of the High Commercial Vehicles in TATA motors.
			\item Presented ideas to the Quality Assurance team to increase efficiency of vehicle production.
 			\end{itemize} 			
\end{itemize}
\vspace{-10pt}
%\paragraph*{Relevant coursework:} 
%Mechanics of Solids, Machine Design, Industrial Engineering, Computational Mechanics, Intro to High-Performance Computing,
\paragraph*{Publications:}
\vspace{-10pt}
\begin{itemize}
\setlength{\itemsep}{8pt}
\setlength{\parskip}{0pt}
\item I. Tembhekar, J. S. Amelang, L. Munk, D. M. Kochmann. \textbf{Automatic adaptivity in the fully-nonlocal quasicontinuum method for coarse-grained atomistic simulations} (under review).
\item  L. Munk, I. Tembhekar, D. M. Kochmann. \textbf{The Constrained Advancing Front (CAF) Algorithm, Mesh adaptivity in the fully-nonlocal 3D quasicontinuum method} (in preparation).
\end{itemize}
\paragraph*{Conference Presentations:}
\vspace{-10pt}
\begin{itemize}
\setlength{\itemsep}{8pt}
\setlength{\parskip}{0pt}
\item \textbf{3D Modeling of Grain Boundaries using a fully-nonlocal and high-performance realization of the quasicontinuum method}, \emph{Engineering Mechanics Institute Conference}, Vanderbilt University, Nashville, TN, May 22-25, 2016.
\end{itemize}
\paragraph*{Teaching Experience:}
\vspace{-10pt}
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\item Teaching Assistant, \textbf{Computational Mechanics} (Fall 2014, Winter 2015)
\item Teaching Assistant, \textbf{Continuum Mechanics} (Winter 2014, Fall 2015, Winter 2016)
\item Teaching Assistant, \textbf{Mechanics of Solids and Structures} (Fall 2013)
\item Teaching Assistant, \textbf{Engineering Mechanics} (Fall 2011)
\end{itemize}
\vspace{-10pt}
\paragraph*{Skills:}
\vspace{-10pt}
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\item Programming Languages: C++, Python, Java, C
\item Software: MATLAB, Mathematica, Paraview, AutoCAD
\end{itemize}
\vspace{-10pt}
\paragraph*{Hobbies:} Tennis, Badminton, Trail running, Hiking, Photography, Indian Classical Music.
\vspace{-10pt}
%\paragraph*{Visa/citizenship status:} On a F1 multiple entry student visa. \\\\
%\textbf{References available upon request}
\end{document}
