\documentclass[10pt,fleqn]{article}

%\usepackage[left=1in, right=1in, top=1.2in, bottom=0.9in,includefoot]{geometry}
\usepackage[left=0.5in, right=0.5in, top=0.5in, bottom=0.5in]{geometry}
%\usepackage{fancyhdr}
\usepackage{algorithm2e}
\usepackage[round]{natbib}
\usepackage{amssymb,amstext,amsmath}
\usepackage{booktabs,graphicx}
\usepackage{bm}
\setlength{\parindent}{0mm}
\setlength{\parskip}{3mm}
\input{defs.tex}

%\pagestyle{fancy}  

%% Custom added packages
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{wrapfig}
\usepackage{sidecap}
\usepackage{hyperref}
%% /Custom added packages

%% Initial setup
\hypersetup{
    %bookmarks=true,         % show bookmarks bar?
    %unicode=false,          % non-Latin characters in Acrobat’s bookmarks
    %pdftoolbar=true,        % show Acrobat’s toolbar?
    %pdfmenubar=true,        % show Acrobat’s menu?
    %pdffitwindow=false,     % window fit to page when opened
    %pdfstartview={FitH},    % fits the width of the page to the window
    %pdftitle={My title},    % title
    pdfauthor={Ishan Tembhekar},     % author
    pdfsubject={Resume_Industry},   % subject of the document
    %pdfcreator={Creator},   % creator of the document
    %pdfproducer={Producer}, % producer of the document
    %pdfkeywords={keyword1} {key2} {key3}, % list of keywords
    %pdfnewwindow=true,      % links in new window
    %colorlinks=false,       % false: boxed links; true: colored links
    linkcolor=red,          % color of internal links (change box color with linkbordercolor)
    citecolor=green,        % color of links to bibliography
    %filecolor=magenta,      % color of file links
    urlcolor=cyan           % color of external links
}
%% /Initial setup


%\renewcommand{\headrulewidth}{0.4pt}
%\fancyfoot[C]{\sffamily \thepage{}}
%\fancyhead[C]{\sffamily\footnotesize \textbf{Ishan Tembhekar}  \hfill Ph No: +16269917232 \\\href{mailto:ishan.tembhekar@caltech.edu}{ishan.tembhekar@caltech.edu} \hfill 1200 E. California Blvd, MC 105-50, Pasadena CA 91125 }
%\fancyhead[RL]{}


\begin{document}
%\thispagestyle{fancy}
\thispagestyle{empty}
%\thispagestyle{fancy}
%\fancyhf{} % clear all header and footer fields
%\fancyfoot[C]{\sffamily\thepage}
%\fancyhead[L]{\sffamily\emph{D.\ M.\ Kochmann}}
%\fancyhead[R]{\sffamily\emph{California Institute of Technology}}
%\renewcommand{\headrulewidth}{0.4pt}
%\vspace{-2cm}
%\sffamily
\begin{center}
%\large %$\mathpzc{Curriculum \ Vitae}$\\[0.4cm] %\emph{Curriculum Vitae}
%\scshape Curriculum  Vitae \upshape\\[0.5cm]
\LARGE \textbf{Ishan Tembhekar} \small \\[0.16cm]
1200 E. California Blvd, MC 105-50, Pasadena CA 91125 \\
Ph No: +16269917232 \\
\href{mailto:ishan.tembhekar@caltech.edu}{ishan.tembhekar@caltech.edu} \hfill
\end{center}
%\begin{center}\small 
%\emph{California Institute of Technology \\
%Graduate Aerospace Laboratories\\ 
%1200 East California Blvd., MC 105-50, Pasadena, CA 91125 \\
%Phone: 626-991-7232}\\[0.27cm]
%\emph{email:} \href{mailto:ishan.tembhekar@caltech.edu}{\emph{ishan.tembhekar}\rmfamily @\sffamily\emph{caltech.edu}} 
%\end{center}
%\paragraph*{Goal:} Seeking a full time position in computational modeling for engineering applications starting Fall 2017
%\paragraph*{Education:}
\textbf{Education:}
\vspace{-25pt}
\begin{center}
\rule{\textwidth}{.4pt}
\end{center}
\vspace{-15pt}
\begin{itemize}
\setlength{\itemsep}{5pt}
\setlength{\parskip}{0pt}
\setlength{\itemindent}{-5mm}
\item[] \textbf{Ph.D.} in Mechanical Engineering\hfill  June-2017(expected)\\
		California Institute of Technology
\item[] \textbf{Master of Science (M.S.)} in Mechanical Engineering \hfill 2014\\
		California Institute of Technology\\
		Cumulative GPA: 4.0/4.0 
\item[] \textbf{Bachelor of Technology (B.Tech.)} in Mechanical Engineering, with a Minor in Computer Science \hfill 2012\\
		Intian Institute of Technology, Gandhinagar\\
		GPA: 9.61/10.0 (Department silver medalist) 
\end{itemize}
\vspace{-5pt}
\textbf{Skills:}
\vspace{-25pt}
\begin{center}
\rule{\textwidth}{.4pt}
\end{center}
\vspace{-15pt}
%\section*{Areas of Interest}
%Mechanics of Solids, Coarse Grain Atomistics, High performance computing
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\itemindent}{-5mm}
\item[] \textbf{Programming Languages}: C++, Python, Java, C
\item[] \textbf{Software}: MATLAB, Mathematica, Paraview, AutoCAD
\item[] \textbf{Relevant coursework}: Mechanics of Solids, Machine Design, Computational Mechanics, Finite Element Modeling, High-Performance Computing
\end{itemize}
%\paragraph*{Relevant coursework:} 
%Mechanics of Solids, Machine Design, Industrial Engineering, Computational Mechanics, Finite Element Modeling, High-Performance Computing \\
\vspace{-5pt}
\textbf{Professional Experience:}
\vspace{-25pt}
\begin{center}
\rule{\textwidth}{.4pt}
\end{center}
\vspace{-15pt}
\begin{itemize}
\setlength{\itemsep}{8pt}
\setlength{\parskip}{0pt}
\setlength{\itemindent}{-5mm}
\item[] \textbf{Industrial Internship}: \emph{TATA Motors, India} \hfill May - July 2010
		    \begin{itemize}
		    \item Studied and observed the assembly line of the High Commercial Vehicles in TATA motors.
			\item Implemented \textbf{\emph{Pokayoke}} or mistake proofing on various recurring defects .
			\item Presented ideas to the Quality Assurance team to increase efficiency of vehicle production.
 			\end{itemize} 			
\end{itemize}
\vspace{-5pt}
\textbf{Research Experience:}
\vspace{-25pt}
\begin{center}
\rule{\textwidth}{.4pt}
\end{center}
\vspace{-15pt}
\begin{itemize}
\setlength{\itemsep}{8pt}
\setlength{\parskip}{0pt}
\setlength{\itemindent}{-5mm}
\item[] \textbf{Graduate Researcher /Teaching Assistant }: \emph{California Institute of Technology} \hfill 2013 - Present
	%	 Advisor: Prof. Dennis Kochmann
		  \begin{itemize}
		  \item Developing computational models and \textbf{numerical tools} for studying plastic deformation mechanisms of nanocrystalline materials.
		  \item Building a \textbf{high-performance parallel C++ code} with efficient threading techniques and a distributed memory realization to reach simulation sizes beyond the scope of current academic understanding.
		 % \item Ongoing research is published in the following research paper: \textbf{Automatic adaptivity in the fully-nonlocal quasicontinuum method for coarse-grained atomistic simulations}, Int. J. Numer. Meth. Eng.
 		  \end{itemize}
\item[] \textbf{Undergraduate Summer Research} : \emph{California Institute of Technology} \hfill May - July 2011
	%	  Advisor: Prof. G. Ravichandran
		   \begin{itemize}
		   \item Examined fracture toughness enhancement by adding elastic heterogeneities in solids  
			\item Designed an innovative mechanism for construction of materials having higher resistance to crack propagation than conventional materials.
			\item Devised and constructed a an \textbf{experimental setup} verify the mechanism with successful results.
 			\end{itemize}
\item[] \textbf{Undergraduate Research Assistant} : \emph{IIT Gandhinagar, India} \hfill August 2011- April 2012	
	%	  Advisor: Prof. N. Ramakrishnan 
		   \begin{itemize}
		   \item Worked on design of a hybrid vehicle with increased fuel efficiency at least rated power
			\item Formed a theoretical framework and constructed a \textbf{basic prototype} of construction of a hybrid vehicle which uses lower rated power than that used in conventional vehicles.
 			\end{itemize} 
\end{itemize}
\vspace{-5pt}
\textbf{Research Publications:}
\vspace{-25pt}
\begin{center}
\rule{\textwidth}{.4pt}
\end{center}
\vspace{-15pt}
\begin{itemize}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\itemindent}{-5mm}
\item[] I. Tembhekar, J. S. Amelang, L. Munk, D. M. Kochmann. \textbf{Automatic adaptivity in the fully-nonlocal quasicontinuum method for coarse-grained atomistic simulations}, Int. J. Numer. Meth. Eng.
\item[] L. Munk, I. Tembhekar, D. M. Kochmann. \textbf{The Constrained Advancing Front (CAF) Algorithm, Mesh adaptivity in the fully-nonlocal 3D quasicontinuum method} (in preparation). 
\end{itemize}
%\paragraph*{Hobbies:} Tennis, Badminton, Trail running, Hiking, Photography, Indian Classical Music.
%\vspace{-10pt}
%\paragraph*{Visa/citizenship status:} On a F1 multiple entry student visa. \\\\
%\textbf{References available upon request}
\end{document}
